\section{Related Work}
\label{sec:related}

\todo{fill in citations in task 11.3.}

\subsection{Memory Poisoning Attacks on LLM Agents}
\label{sec:related:attacks}

MINJA, AgentPoison, and A-MemGuard established that shared vector
memory is a viable attack surface for multi-agent LLM systems. MINJA
targets the retrieval layer directly by crafting high-similarity
trigger documents; AgentPoison adds a learned backdoor that activates
on a semantic trigger; A-MemGuard proposes a defensive retrieval
filter but operates per-query without temporal context.
\todo{cite MINJA, AgentPoison, A-MemGuard.}

\subsection{Decentralized Task Allocation in Multi-Agent Systems}
\label{sec:related:alloc}

Classical approaches include contract-net protocols and Dec-POMDP
solvers. More recent work on LLM-based task allocation (AutoGen,
MetaGPT, CrewAI) delegates coordination to a privileged planner agent;
this centralizes trust and re-introduces the very single-point-of-
failure that multi-agent systems were meant to avoid.
\todo{cite contract-net, Dec-POMDP surveys, AutoGen, MetaGPT.}

\subsection{Online Change-Point Detection and Forecasting}
\label{sec:related:cpd}

BOCPD (Adams \& MacKay, 2007) provides a principled run-length
posterior with $O(T)$ memory. Chronos-2 (2024) is a pretrained
probabilistic time-series forecaster whose zero-shot predictive
distribution we use as a temporal prior on agent behavior.
\todo{cite BOCPD, Chronos-2.}

\subsection{Runtime Monitoring for LLM Agents}
\label{sec:related:monitoring}

Prior runtime monitors (NeMo Guardrails, LlamaGuard, constitutional AI
classifiers) focus on content-level filtering at the input and output
boundary. They are complementary to \sys{}: they answer ``is this
specific message safe?'' while \sys{} answers ``has this agent's
behavior drifted over the last $k$ steps?''.
\todo{cite NeMo Guardrails, LlamaGuard.}
