\section{System Design}
\label{sec:system}

\todo{architecture figure + longer prose.}

\sys{} sits between a LangGraph~\citep{langgraph}-orchestrated agent
pool, built on LangChain~\citep{langchain} primitives, and a shared
Chroma~\citep{chromadb} vector memory. It exposes three control-plane
components:

\paragraph{Behavioral Monitor (\cref{sec:methodology:signals}).}
For every PR-handling step, each agent emits six scalar signals:
response latency, retrieval count, output token count, KL
divergence against a pre-attack baseline distribution, tool-call
frequency, and memory-query entropy. The monitor persists these
signals to SQLite (dev) or PostgreSQL (prod) for offline analysis
and streams them to the Temporal Health Scorer.

\paragraph{Temporal Health Scorer (\cref{sec:methodology:detector}).}
The scorer combines two detectors on the dominant signal
(KL divergence): a Bayesian Online Change-Point
Detector~\citep{adams2007bocpd} that flags regime shifts with
calibrated run-length posteriors, and a Chronos-2~\citep{chronos}
probabilistic forecaster that supplies an expected-range prior. A
positive detection from either branch decrements the agent's health
score; a sustained normal regime lets the score recover.

\paragraph{Decentralized Task Allocator (\cref{sec:methodology:alloc}).}
New PRs are offered via a lightweight contract-net-style negotiation
protocol~\citep{contractnet}; each agent submits a bid equal to its
static capability for the task type multiplied by its current health
score. The allocator assigns the task to the highest bid above a
configurable threshold, or escalates to a human reviewer when no
agent clears the threshold. A drifting agent's health score drops,
its bid falls, and work routes away from it automatically, without
a centralized kill-switch.

\paragraph{Human Escalation Layer.}
When the aggregate health score across the pool drops below a
configurable threshold, or when change-points cluster in a short
window, the system raises a reviewer alert through the FastAPI
dashboard (Phase 8) rather than silently quarantining agents.
