\section{Methodology}
\label{sec:methodology}

\todo{formalize each subsection.}

\subsection{Behavioral Signals}
\label{sec:methodology:signals}

Let $s_{a,t} \in \mathbb{R}^6$ denote the signal vector for agent $a$
at PR-handling step $t$. The six components are:
\begin{enumerate}
  \item \textbf{Tool-call entropy} $H(\pi_{\text{tool}})$ over the
  agent's empirical tool distribution in a sliding window.
  \item \textbf{Decision latency} (median wall-clock time per step).
  \item \textbf{Memory-query entropy} $H(\pi_{\text{query}})$ over the
  embedding cluster IDs that the agent retrieved.
  \item \textbf{KL divergence} $\kldiv(p_t \parallel p_0)$ of the
  current signal distribution against a pre-attack baseline.
  \item \textbf{Retrieval-hit rate} (fraction of memory queries whose
  top-$k$ contained a relevant document).
  \item \textbf{Action-repetition rate} over the last $w$ steps.
\end{enumerate}

\subsection{BOCPD + Chronos Ensemble}
\label{sec:methodology:detector}

We apply a Bayesian Online Change-Point Detector
(BOCPD)~\citep{adams2007bocpd} to the KL divergence stream, using a
Gaussian observation model with conjugate Normal-Gamma prior. The
run-length posterior $p(r_t \mid s_{1:t})$ collapses when a change
point is detected; we flag step $t$ whenever
$p(r_t = 0 \mid s_{1:t}) > \tau_{\text{cpd}}$.

In parallel, a Chronos-2-Small forecaster~\citep{chronos} is
conditioned on the last $L=64$ KL divergence samples and emits
quantile predictions
$\{\hat{q}_{0.1}, \hat{q}_{0.5}, \hat{q}_{0.9}\}$ for the next step.
An observation outside $[\hat{q}_{0.1}, \hat{q}_{0.9}]$ is flagged.
The two detectors are combined with an OR aggregation; the system
health score is decremented on either branch firing.

\subsection{Advance Warning Time}
\label{sec:methodology:awt}

For each run we define Advance Warning Time as
\begin{equation}
  \awt{} = t_{\text{first\_flagged}} - t_{\text{injection}},
\end{equation}
where $t_{\text{injection}}$ is the ground-truth step at which the
poisoning payload was written to memory. $\awt{} < 0$ means the
detector fired before the payload took effect (the desired regime);
$\awt{} = 0$ means concurrent detection (Pivot~A);
$\awt{} > 0$ means the detector fired only after downstream damage.

\subsection{Health-Weighted Allocation}
\label{sec:methodology:alloc}

The allocation layer is a shallow contract-net
variant~\citep{contractnet}; a Dec-POMDP view of the underlying
coordination problem is given by~\citet{decpomdp}. Agent $a$'s bid
for PR $j$ is
\begin{equation}
  c_{a,j} = \alpha \cdot \text{queue\_depth}_a + \beta \cdot (1 - h_a),
\end{equation}
where $h_a \in [0, 1]$ is the rolling health score. An agent whose
health score drops to zero becomes non-competitive and receives no new
work until it recovers.
